%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Working  experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Cofounder} % Job title
{Arengu} % Organization
{A Coru単a} % Location
{May. 2018 - Present} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Business and ethical marketing development in a startup with 7 employees.}
\item {Main \textbf{\href{https://arengu.com/}{Arengu}} frontend developer, design and UX interaction designer.}
\item {Experience in funding rounds, startups accelerators and working with investors.}
\end{cvitems}
}

\cventry
{Front end developer} % Job title
{MOBGEN} % Organization
{A Coru単a} % Location
{Oct. 2016 - May. 2018} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Managing frontend team in 
\textbf{\href{https://halo.mobgen.com/info/}{HALO}}, a backend as a service
platform to help in mobile apps development.}
\item {Using React in a complex Redux app with Material UI among other 
libraries like React Virtualized or Redux Saga.}
\item {Been part of an international team providing services for big clients as 
AEGON, ABN AMRO or KPN.}
\end{cvitems}
}

\cventry
{Full stack web developer} % Job title
{Imatia Innovation} % Organization
{A Coru単a} % Location
{Feb. 2016 - Oct. 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Developing a platform for trade logistics and forecast 
calculation for Inditex, one of the biggest textile companies in the world.}
\item {The application was developed using Java + Spring in the backend and
Backbone + JQuery and other libraries in the frontend.}
\end{cvitems}
}

\cventry
{Cofounder} % Job title
{VACmatch} % Organization
{A Coru単a} % Location
{Oct. 2014 - Feb. 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Developing a web application and mobile hybrid app for sport management 
using technologies like Scala, React or Reflux.}
\item {Using continuous integration systems (Jenkins and Travis) and Git 
repositories doing code review with Gerrit and GitHub.}
\item {Working on business strategies based on Free Software.}
\end{cvitems}
}


%------------------------------------------------    

\end{cventries}
