%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Advocacy groups}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------
\cventry
{Privacy and internet freedom hacktivist} % Affiliation/role
{Trackula}  
{A Coruña / Madrid} % Location
{Sep. 2017 - Present} % Date(s)
{ % Description(s) of experience/contributions/knowledge
\begin{cvitems}
\item {Research and test actions to advocate for privacy issues in real environments.}
\item {Development of apps to raise awareness around privacy and internet freedom.}
\item {Working with international partners to fight against GDPR infringements.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Community organizer} % Affiliation/role
{Grupo de Programadores y Usuarios de Linux (GPUL)} % Organization/group
{A Coruña} % Location
{Feb. 2012 - Present} % Date(s)
{ % Description(s) of experience/contributions/knowledge
\begin{cvitems}
\item {Community creation in one of the bigests Linux Users Group  in Spain with more than 500 members.}
\item {Managing meetups and workshops to promote free software, open 
source hardware and free culture.}
\item {Leading international conferences organization with Free Software 
communities like KDE, GNOME or X.org.}
\item {Developing and coordinating 
\textbf{\href{http://labs.gpul.org/}{GPUL Labs}} and \textbf{\href{https://corunahacks.gpul.org/}{CoruñaHacks}}, working with many companies and startups as Igalia or CartoDB.}
\item {Collaboration with NGOs and other associations, helping them to switch to
Free Software.}
\item {Lobby to add open technology practices to local and regional institutions.}
\end{cvitems}
}

%------------------------------------------------
\cventry
{Community organizer} % Affiliation/role
{CoruñaDevelopers, CoruñaJS and other communities}  
{A Coruña} % Location
{Feb. 2012 - Present} % Date(s)
{ % Description(s) of experience/contributions/knowledge
\begin{cvitems}
\item {Spread free software technologies inside other groups}
\item {Collaboration between different communities to promote privacy and open technologies.}
\item {Contacts with other groups, GDGs, galician linux users groups and other 
spanish free software groups, open source makers and transparency entities as Civio or OpenKratio.}
\end{cvitems}
}


\end{cventries}
