%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Given presentations}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}


%------------------------------------------------

\cventry
{\href{https://flisol2019acoruna.wordpress.com/}{Web}} % Role
{Flisol} % Event
{A Coruña} % Location
{Apr. 2019} % Date(s)
{ % Description(s)
\begin{cvitems}
\item {\textbf{1984 is coming. Tools to keep your privacy in internet} Talking about privacy, how, why and who is spying us in the technology world and some tips to improve our privacy in real world and in the internet, plugins and best practices.
}
\end{cvitems}
}


%------------------------------------------------

\cventry
{\href{https://www.tabakalera.eu/en/summerlab-2018-meeting-citizen-research-civic-use-of-technology}{Web}} % Role
{Tabakalera SummerLab 2018} % Event
{San Sebastián} % Location
{Jul. 2018} % Date(s)
{ % Description(s)
\begin{cvitems}
\item {\textbf{1984 is coming. Privacy in the real world} Talking about privacy, how, why and who is spying us in the technology world and some tips to improve our privacy in the real world, outside computers and the internet.
}
\end{cvitems}
}

%------------------------------------------------

\cventry
{\href{http://galicia2017.librecon.io/}{Web}} % Role
{LibreCon} % Event
{Santiago de Compostela} % Location
{Oct. 2017} % Date(s)
{ % Description(s)
\begin{cvitems}
\item {\textbf{1984 is coming. Privacy as business model?} Gives a vision of some companies with business models based on privacy and some tips to improve clients privacy as developers or companies.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{\href{https://lignux.com/material-de-las-ii-jornadas-de-acercamiento-teorico-practico-al-software-y-hardware-libre-2015/}{Web 2015},
\href{https://lignux.com/material-de-las-iii-jornadas-de-acercamiento-teorico-practico-al-software-y-hardware-libre-2016/}{Web 2016}} 
{Jornadas de acercamiento teórico-práctico al software y hardware libre en
el ámbito socioeducativo} % Event
{Ourense} % Location
{2016} % Date(s)
{ % Description(s)
\begin{cvitems}
\item {\textbf{What I am doing in the Open Source world?} Introductory talk
about free software and how to contribute to
communities.}
\item {\textbf{How much to reach 1984?} Privacy introduction in tech.}
\end{cvitems}
}


%------------------------------------------------

\cventry
{\href{https://www.kde-espana.org/akademy-es2015/index.php}{Web}} % Role
{Akademy-es} % Event
{A Coruña} % Location
{Jul. 2015} % Date(s)
{ % Description(s)
\begin{cvitems}
\item {\textbf{Free software driving startups.} Free sofware alternatives for 
startups and Free Software business models lean on successful stories.}
\\ \\
You can see more talks \textbf{\href{https://github.com/castrinho8/my-talks}{in this link}}.
\end{cvitems}
}

%------------------------------------------------

\end{cventries}
