%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Projects and hosted conferences}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{National technology conference} % Institution
{Atlántica Conf} % Degree
{A Coruña} % Location
{Oct. 2019} % Date(s)
{ % Description(s) bullet points
\begin{cvitems}
Planing a medium size conference about open source technologies and best development practices in the nordwest of Spain.
\end{cvitems}
}

%------------------------------------------------

\cventry
{Free software comunities conference} % Institution
{\href{https://trackula.org/en/page/cfp-eslibre-2019/}{esLibre 2019 - Privacy, decentralization and Information sovereignty devroom}} % Degree
{Granada} % Location
{Jun. 2019} % Date(s)
{ % Description(s) bullet points
\begin{cvitems}
Trackula is going to manage and coordinate a devroom in esLibre conference, a community based congress about free and open source technologies about privacy and decentralization.
\end{cvitems}
}

%------------------------------------------------

\cventry
{X.org international conference} % Institution
{\href{https://xdc2018.x.org/}{XDC 2018}} % Degree
{A Coruña} % Location
{Sep. 2018} % Date(s)
{ % Description(s) bullet points
\begin{cvitems}
Hosted main conference from X.org community where most important developers in open source graphic systems meet once a year. \\
In 2017 this event took place in Google offices in Silicon Valley and this year we hosted it in Spain with sponsors like Google, NVIDIA, Valve, Intel or AMD among others.
\end{cvitems}
}

%------------------------------------------------

\cventry
{KDE international conference} % Institution
{\href{https://akademy.kde.org/2015}{Akademy 2015}} % Degree
{A Coruña} % Location
{Jul. 2015} % Date(s)
{ % Description(s) bullet points
\begin{cvitems}
Hosted main conference from KDE community where developers from all over the world in KDE linux desktop community meet once a year. In 2015 we hosted it in Spain for one week and with sponsors like OpenSuse, The QT Company or Google among others.
\end{cvitems}
}

%------------------------------------------------

\cventry
{GNOME international conference} % Institution
{\href{http://lacomunera.net/2012/08/01/guadec-2012/}{GUADEC 2012}} % Degree
{A Coruña} % Location
{Jul. 2012} % Date(s)
{ % Description(s) bullet points
\begin{cvitems}
Hosted main conference from GNOME community where developers from all over the world in GNOME linux desktop community meet once a year.
\end{cvitems}
}

%------------------------------------------------

\cventry
{Final degree project} % Institution
{\href{https://github.com/vacmatch/vacmatch-mobile}{VACmatch Mobile}} % Degree
{A Coruña} % Location
{Dic. 2015 - Present} % Date(s)
{ % Description(s) bullet points
\begin{cvitems}
\item {Web application to manage sport reports, helping referees to sync all 
results and statistics in the match with the competition manager web page in 
real time and even offline.}
\item {An hybrid mobile application built following TDD with React, PouchDB and 
Jest, deployed as a Docker image under continuous integration with Travis.}
\end{cvitems}
}

\end{cventries}
